A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions

### 2016-03-10 MSRChallenge2016.tex
small change in phrasing

\vspace{1ex}
\noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
a similar set of questions in 5 projects. In this paper we have studied a much larger dataset~\cite{dyer2013} with 380,125 repositories, and we also study
replacements, omitted from Zhong and Su's analysis.  Barr et al.~\cite{Barr14fse} studied changes to
Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
certain types of program repair, an orthogonal
concern. Kim et al.~\cite{kim2013} manually analyze 
changes to Java programs to inform an automated repair
technique, and show that doing so results in higher-quality repairs; 
we study their templates heuristically on
a different dataset. Their results motivate
studies of human repairs, as it may result in better patches.
Long and Rinard learn probabilistic models from bug fixes to C
code~\cite{Long2016}. Our analysis is significantly less precise and does not
inform a new technique.  Rather, it serves as a starting
point for research on the repair of Java bugs.

>>>>

\vspace{1ex}
\noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
a similar set of questions in 5 projects. In this paper we have studied a much larger dataset~\cite{dyer2013} with 380,125 repositories; we have studied more statement types, and we have studied replacements, omitted from Zhong and Su's analysis.  Barr et al.~\cite{Barr14fse} studied changes to
Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
certain types of program repair, an orthogonal
concern. Kim et al.~\cite{kim2013} manually analyze 
changes to Java programs to inform an automated repair
technique, and show that doing so results in higher-quality repairs; 
we study their templates heuristically on
a different dataset. Their results motivate
studies of human repairs, as it may result in better patches.
Long and Rinard learn probabilistic models from bug fixes to C
code~\cite{Long2016}. Our analysis is significantly less precise and does not
inform a new technique.  Rather, it serves as a starting
point for research on the repair of Java bugs.
